j_play

### 2020-12-02 scripts/BCOR_combo.Rmd
Effect Size - First Structure is there!

```{r setup, include = FALSE, echo = FALSE, warning = FALSE}
library("papaja")
r_refs("r-references.bib")
library(here)
library(tidyverse)
library("readxl")
library(janitor)

@@

BCdatastripped <- BCdata %>% 
    #Makayla & Janette - may want to include more columns here with the select for our global "BCdatastripped" df
    select("SCHOOL_YEAR", 
         "DATA_LEVEL", 
         "SPECIAL_NEEDS_CODE", 
         "NUMBER_OF_STUDENTS", 
         "PUBLIC_OR_INDEPENDENT",
         "DISTRICT_NUMBER") %>% 
  filter(SPECIAL_NEEDS_CODE != "M",
         SPECIAL_NEEDS_CODE != "J",
         SPECIAL_NEEDS_CODE != "N") %>% 
    mutate(SPECIAL_NEEDS_CODE = fct_recode(SPECIAL_NEEDS_CODE,
                          "Physically Dependent" = "A",
                          "Deafblind" = "B",
                          "Moderate+ ID" = "C",
                          "Chronic Health Impairment" = "D",
                          "Visual Impairment" = "E",
                          "Deaf or Hard of Hearing" = "F",
                          "Autism" = "G",
                          "Intensive Behavioural Need" = "H",
                          "Mild ID" = "K",
                          "Learning Disability" = "Q",
                          "Gifted" = "P",
                          "Mild Behavioural Need" = "R"),
           SCHOOL_YEAR = as.factor(SCHOOL_YEAR), 
           NUMBER_OF_STUDENTS = as.integer(NUMBER_OF_STUDENTS),
           SCHOOL_YEAR = as.numeric(SCHOOL_YEAR)) %>% 
  filter(SCHOOL_YEAR >= 9)

@@

combined <- fresh_primo %>% 
  as_tibble() %>% 
    mutate(ORheadcount = fct_recode(disability,
                          "Deafblind" = "DEAF-BLINDNESS",
                          "Moderate+ ID" = "INTELLECTUAL DISABILITY",
                          "Chronic Health Impairment" = "EMOTIONAL DISTURBANCE",
                          "Visual Impairment" = "VISUAL IMPAIRMENT",
                          "Deaf or Hard of Hearing" = "HEARING IMPAIRMENT",
                          "Autism" = "AUTISM",
                          "Mild ID" = "INTELLECTUAL DISABILITY")) %>% 
  filter(ORheadcount == "Autism") %>% 
  group_by(year) %>% 
  summarise(frequency = sum(frequency))

BCAutism <- BCprovincial %>% 
  filter(SPECIAL_NEEDS_CODE == "Autism")

# BCprovincial <- BCdatastripped %>% 
#   filter(DATA_LEVEL == "PROVINCE LEVEL",
#          PUBLIC_OR_INDEPENDENT == "PROVINCE - Total")  %>% 
#   mutate(Public_population = BCpopulation$TOTAL_ENROLMENT[SCHOOL_YEAR-8],
#          prevalence = NUMBER_OF_STUDENTS/Public_population) %>% 
#   mutate(SCHOOL_YEAR = SCHOOL_YEAR+1995)

ggplot() +
  geom_smooth(data = combined, aes(x = year, y = frequency), color = "cornflowerblue") +
  geom_smooth(data = BCAutism, aes(x = SCHOOL_YEAR, y = NUMBER_OF_STUDENTS), color = "red") +
  labs(title = "Visualizing BC and Oregon Headcount of Autism Spectrum Disorder",
        x = "School Year",
        y = "Headcount")

>>>>

```{r setup, include = FALSE, echo = FALSE, warning = FALSE}
library("papaja")
r_refs("r-references.bib")
library(here)
library(tidyverse)
library("readxl")
library(janitor)
library(esc)

@@

BCdatastripped <- BCdata %>% 
    #Makayla & Janette - may want to include more columns here with the select for our global "BCdatastripped" df
    select("SCHOOL_YEAR", 
         "DATA_LEVEL", 
         "SPECIAL_NEEDS_CODE", 
         "NUMBER_OF_STUDENTS", 
         "PUBLIC_OR_INDEPENDENT",
         "DISTRICT_NUMBER") %>% 
  filter(SPECIAL_NEEDS_CODE != "M",
         SPECIAL_NEEDS_CODE != "J",
         SPECIAL_NEEDS_CODE != "N") %>% 
    mutate(SPECIAL_NEEDS_CODE = fct_recode(SPECIAL_NEEDS_CODE,
                          "Physically Dependent" = "A",
                          "Deafblind" = "B",
                          "Moderate+ ID" = "C",
                          "Chronic Health" = "D",
                          "Visual Impairment" = "E",
                          "Deaf or Hard of Hearing" = "F",
                          "Autism" = "G",
                          "High Behavioural Need" = "H",
                          "Mild ID" = "K",
                          "Learning Disability" = "Q",
                          "Gifted" = "P",
                          "Mild Behavioural Need" = "R"),
           SCHOOL_YEAR = as.factor(SCHOOL_YEAR), 
           NUMBER_OF_STUDENTS = as.integer(NUMBER_OF_STUDENTS),
           SCHOOL_YEAR = as.numeric(SCHOOL_YEAR)) %>% 
  filter(SCHOOL_YEAR >= 9)

@@

combined <- fresh_primo %>% 
  as_tibble() %>% 
    mutate(ORheadcount = fct_recode(disability,
                          "Deafblind" = "DEAF-BLINDNESS",
                          "Moderate+ ID" = "INTELLECTUAL DISABILITY",
                          "High Behavioural Need" = "EMOTIONAL DISTURBANCE",
                          "Visual Impairment" = "VISUAL IMPAIRMENT",
                          "Deaf or Hard of Hearing" = "HEARING IMPAIRMENT",
                          "Autism" = "AUTISM",
                          "Mild ID" = "INTELLECTUAL DISABILITY")) %>% 
  filter(ORheadcount == "High Behavioural Need") %>% 
  group_by(year) %>% 
  summarise(frequency = sum(frequency))

BCAutism <- BCprovincial %>% 
  filter(SPECIAL_NEEDS_CODE == "High Behavioural Need")

ggplot() +
  geom_smooth(data = combined, aes(x = year, y = frequency, color = "Oregon")) +
  geom_smooth(data = BCAutism, aes(x = SCHOOL_YEAR, y = NUMBER_OF_STUDENTS, color = "British Columbia"), se = FALSE) +
  labs(title = "BC and Oregon Headcount of Students with Chronic Health Conditions",
        x = "School Year",
        y = "Headcount",
       color = "Legend",
        scale_color_manual(labels = c("Oregon", "British Columbia"), values = c("blue", "red")))

``` {r calculatingES}

ESdata <- BCdatastripped %>% 
  filter(SPECIAL_NEEDS_CODE == "High Behavioural Need",
         DATA_LEVEL == "DISTRICT LEVEL",
         PUBLIC_OR_INDEPENDENT == "BC Public School",
         DISTRICT_NUMBER == "036")  %>% 
  mutate(Public_population = BCpopulation$TOTAL_ENROLMENT[SCHOOL_YEAR-8],
         prevalence = NUMBER_OF_STUDENTS/Public_population) %>% 
  mutate(SCHOOL_YEAR = SCHOOL_YEAR+1995,
         pre16 = ifelse(SCHOOL_YEAR <= 2016, "before16", "after16")) %>%
  group_by(pre16) %>% 
  pivot_wider(
    names_from = pre16,
    values_from = prevalence
  )

presup <- ESdata %>% 
  drop_na(before16) %>% 
  select(before16)
as.numeric(unlist(presup))

postsup <- ESdata %>% 
  drop_na(after16) %>% 
  select(after16)
as.numeric(unlist(postsup))

presup_mean <- sapply(presup, mean)
presup_sd <- sapply(presup, sd)
postsup_mean <- sapply(postsup, mean)
postsup_sd <- sapply(postsup, sd)

esc_mean_sd(grp1m = presup_mean, grp1sd = presup_sd, grp1n = 13, grp2m = postsup_mean, grp2sd = postsup_sd, grp2n = 3, es.type = "g")
